{\fontfamily{ptm}\selectfont Lorum ipsum}

### 2025-07-03 Notebook LaTEX/SAGD Under Interpolation/main.tex
>w<, updates

        \begin{definition}[similar triangle representation of NAPG]\;\label{def:st-method}\\
            Let $(\alpha_k)_{k \ge 0}$ be an R-WAPG sequence. 
            Suppose that the base case $v_{-1}, x_{k - 1}\in \RR^n$ is given to initialize the algorithm. 
            Then the algorithm produces the sequence of iterates $(y_k, x_k, v_k)_{k \ge 0}$ and auxiliary parameter sequence $L_k, \tau_k$ satisfying these inequalities: 
            \begin{align*}
                & \tau_k = L_k(1 - \alpha_k)(L_k\alpha_k - \mu)^{-1}, 
                \\
                & y_k = (1 + \tau_k)^{-1} v_{k - 1} + \tau_k (1 + \tau_k)^{-1} x_{k - 1},
                \\
                & D_f(x_k, y_k) \le L_k/2\Vert x_k - y_k\Vert^2, 
                \\
                & x_k = T_{L_k}(y_k),
                \\
                & v_k = x_{k - 1} + \alpha_k^{-1}(x_k - x_{k - 1}). 
            \end{align*} 
        \end{definition}
        The following theorems are critical in analyzing the behavior of algorithm in Definition \ref{def:st-method}. 
        \begin{theorem}[proximal gradient inequality]\label{thm:pg-ineq}
            Let function $F$ satisfies Assumption \ref{ass:smooth-plus-nonsmooth}, so it's $\mu \ge 0$ strongly convex. 
            For all $x\in \RR^n$, define $x^+ = T_L(x)$, then there exists a $B \ge 0$ such that $D_f(x^+, x) \le B/2 \Vert x^+ - x\Vert^2$. 
            Then, for all $z \in \RR^n$ it satisfies proximal gradient inequality at point $x$:  
            \begin{align*}
                0&\le F(z) - F(x^+) - \frac{B}{2}\Vert z - x^+\Vert^2  + \frac{B - \mu}{2}\Vert z - x\Vert^2
                \\
                &=  F(z) - F(x^+) - \langle B(x - x^+), z - x\rangle
                - \frac{\mu}{2}\Vert z - x\Vert^2
                - \frac{B}{2}\Vert x - x^+\Vert^2. 
            \end{align*}
            Since $f$ is assumed to be $L$ Lipschitz smooth, the above condition is true for all $x, y \in \RR^n$ for all $B \ge L$. 
        \end{theorem}
        \begin{remark}
            The theorem is the same as in Nesterov's book \cite[Theorem 2.2.13]{nesterov_lectures_2018}, but with the use of proximal gradient mapping and proximal gradient instead of project gradient hence making it equivalent to the theorem in Beck's book \cite[Theorem 10.16]{beck_first-order_2017}. 
            The only generalization here is parameter $B$ which made to accommodate algorithm that implements Definition \ref{def:st-method} with some line search routine. 
        \end{remark}
        \begin{theorem}[Jensen's inequality]\label{thm:jesen}
            Let $F: \RR^n \rightarrow \overline \RR$ be a $\mu \ge 0$ strongly convex function. 
            Then, it is equivalent to the following condition. 
            For all $x, y \in \RR^n$, $\lambda \in (0, 1)$ it satisfies the inequality 
            \begin{align*}
                (\forall \lambda \in [0, 1])\; 
                F(\lambda x + (1 - \lambda)y) \le \lambda F(x) + (1 - \lambda)F(y) -\frac{\mu\lambda(1 - \lambda)}{2} \Vert y - x\Vert^2. 
            \end{align*}
        \end{theorem}
        \begin{remark}
            If $x, y$ is out of $\dom F$, the inequality still work by convexity. 
        \end{remark}

    % \subsection{A compact argument for the convergence of NAPG with proximal gradient}
    %     Here, the abbreviation ``NAPG" stands for ``Nesterov Acceleration Proximal Gradient". 
    %     It's made in acknowledgement of Algorithm 2.2.36 in Nesterov's book \cite{nesterov_lectures_2018} and its extension known as FISTA in the literature.
    %     The following theorem provides a complete proof for the convergence rate of algorithms implementing Definition \ref{def:st-method}, which is equivalent to NAG, or NAPG. 
    %     It made use of Definition \ref{def:rwapg-seq} which accommodates a relaxed sequence compared to the usual sequence that gives the optimal convergence rate. 
    %     \begin{theorem}[one step convergence claim of NAPG]\label{thm:onestep-napg-cnvg}
    %         Let $F = f + g$ satisfies Assumption \ref{ass:smooth-plus-nonsmooth} for some $L > \mu \ge 0$. 
    %         Let the sequence $(\alpha_k)_{k \ge0}$ be an R-WAPG sequence (Definition \ref{def:rwapg-seq}). 
    %         Suppose that the iterates sequence $(x_k, y_k, v_k)_{k \ge 0}$ satisfy NAPG in similar triangle form (Definition \ref{def:st-method}) with initial guesses $v_{-1}, x_{-1} \in \RR^n$. 
    %         Then for all $k \ge 1$, the following inequality is true for all $\bar x \in \RR^n$: 
    %         \begin{align*}
    %             & - F(\bar x) + F(x_k) + \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
    %             \\
    %             & \le \max\left(1, \frac{L_k\rho_{k - 1}}{L_{k - 1}}\right)(1 - \alpha_k)\left(
    %                 F(x_{k - 1}) - F(\bar x) 
    %                 + \frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2
    %             \right). 
    %         \end{align*}
    %         If in addition, we choose $\alpha_0 = 1$, and let $x_{-1} = v_{-1}$, then a base case of the inequality is: 
    %         \begin{align*}
    %             F(x_{0}) - F(\bar x) + \frac{L_0}{2}\Vert \bar x - x_{0}\Vert^2 
    %             &\le \frac{L_0 - \mu}{2}\Vert \bar x - v_{-1}\Vert^2. 
    %         \end{align*}
    %     \end{theorem}
    %     \begin{proof}
    %         The proof is very intense algebraically hence before we step into it, we present the following intermediate results in advance to their proofs given at the end. 
    %         \par
    %         For all $k \ge 0$, define $z_k = \alpha_k \bar x + (1 - \alpha_k)x_{k - 1}$. 
    %         \begin{itemize}
    %             \item [(a)] Theorem \ref{thm:pg-ineq}, with $z = z_k$, $k \ge 0$. We can use it because $F = f + g$ satisfies Assumption \ref{ass:smooth-plus-nonsmooth}. 
    %             \item [(b)] Jensen's inequality (Theorem \ref{thm:jesen}), with $z = z_k$, for $k \ge 0$. We can use it because $F$ is $\mu \ge 0$ strongly convex. 
    %             \item [(c)] Definition \ref{def:rwapg-seq} which has $\rho_k(1 - \alpha_{k + 1})\alpha_k^2 = \alpha_{k + 1}(\alpha_{k + 1} - \mu/L_k)$ for $k \ge 0$.
    %             \item [(d)] The equality $z_k - y_k = (L_k - \mu)^{-1}((L_k\alpha_k - \mu)(\bar x - v_k) + \mu(1 - \alpha_k)(\bar x - x_{k - 1}))$ for all $k \ge 0$, it comes from Definition \ref{def:st-method}. 
    %             \item [(e)] The equality $z_k - x_k = \alpha_k(\bar x - v_k)$ for all $k \ge 0$ it comes from Definition \ref{def:st-method}. 
    %             \item [(f)] Using basic algebra, we have the following equality: 
    %             \begin{align*}
    %                 (\forall k \ge 1)\; \frac{1}{2}\left(
    %                     \frac{\mu^2(1 - \alpha_k)^2}{L_k - \mu} - \mu \alpha_k(1 - \alpha_k)
    %                 \right) &= 
    %                 \frac{(\alpha_k - 1)\mu(L_k\alpha_k - \mu)}{2(L_k - \mu)}. 
    %             \end{align*}
    %             \item [(g)] Using (c), we have the following equality: 
    %             \begin{align*}
    %                 (\forall k \ge 1)\; 
    %                 \frac{1}{2}\left(
    %                     \frac{(L_k\alpha_k - \mu)^2}{L_k - \mu} - 
    %                     \alpha_{k - 1}^2\rho_{k - 1}L_k(1 - \alpha_k)
    %                 \right)
    %                 &= 
    %                 \frac{\mu(L_k\alpha_k - \mu)(\alpha_k - 1)}{2(L_k - \mu)}. 
    %             \end{align*}
    %             \item [(h)] Definition \ref{def:rwapg-seq} determine the inequality: 
    %             \begin{align*}
    %                 (\forall k \ge 1)\; \frac{\mu(L_k\alpha_k - \mu)(\alpha_k - 1)}{2(L_k - \mu)} &\le 0.   
    %             \end{align*}
    %         \end{itemize}
    %         With intermediate results (a) to (h), presented above, the proof of the theorem come smoothly from a chain of inequalities and equalities. 
    %         The overall proof now follows. 
    %         Start with the (a), the proximal gradient inequality it has: 
    %         \begin{align*}
    %             0 &\le F(z_k) - F(x_k) - \frac{L_k}{2}\Vert z_k - x_k\Vert^2 + \frac{L_k - \mu}{2}\Vert z_k - y_k\Vert^2
    %             \\
    %             &\underset{\text{(b)}}{\le}
    %             \alpha_k F(\bar x) + (1 - \alpha_k)F(x_{k - 1}) - F(x_k) \\
    %                 &\quad 
    %                 - \frac{\mu\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2
    %                 - \frac{L_k}{2}\Vert z_k - x_k\Vert^2 + \frac{L_k - \mu}{2}\Vert z_k - y_k\Vert^2. 
    %         \end{align*}
    %         Using the chain of equality below: 
    %         {\footnotesize
    %         \begin{align*}
    %             &- \frac{\mu\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2
    %             + \frac{L_k - \mu}{2}\Vert z_k - y_k\Vert^2
    %             \\
    %             &\underset{\text{(d)}}{=} 
    %             -\frac{\mu\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2\\ 
    %                 &\quad +
    %                 \frac{L_k - \mu}{2}
    %                 \left\Vert 
    %                     \frac{L_k\alpha_k - \mu}{L_k - \mu}(\bar x - v_{k - 1}) + 
    %                     \frac{\mu(1 - \alpha_k)}{L_k - \mu}(\bar x - x_{k - 1})
    %                 \right\Vert^2
    %             \\
    %             &= 
    %             - \frac{\mu\alpha_k(1 - \alpha_k)}{2}\Vert \bar x - x_{k - 1}\Vert^2\\&\quad 
    %                 + \frac{(L_k\alpha_k - \mu)^2}{2(L_k - \mu)} \Vert \bar x - v_{k - 1}\Vert^2
    %                 + \frac{\mu^2(1 - \alpha_k)^2}{2(L_k - \mu)} \Vert \bar x - x_{k - 1}\Vert^2
    %                 + \frac{(L_k\alpha_k - \mu)\mu(1 - \alpha_k)}{L_k - \mu}\langle \bar x - x_{k - 1}, \bar x - v_{k - 1}\rangle
    %             \\
    %             &= \left(
    %                 \frac{\mu^2(1 - \alpha_k)^2}{2(L_k - \mu)} - \frac{\mu\alpha_k(1 - \alpha_k)}{2}
    %             \right)\Vert \bar x - x_{k - 1}\Vert^2
    %             + 
    %             \left(
    %                 \frac{(L_k\alpha_k - \mu)^2}{2(L_k - \mu)}
    %                 - \frac{\alpha_{k - 1}^2L_k \rho_{k - 1}(1 - \alpha_k)}{2}
    %             \right)\Vert \bar x - v_{k - 1}\Vert^2 \\ &\quad 
    %                 + \frac{\alpha_{k - 1}^2L_k \rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
    %                 + \frac{(L_k\alpha_k - \mu)\mu(1 - \alpha_k)}{L_k - \mu}\langle \bar x - x_{k - 1}, \bar x - v_{k - 1}\rangle
    %             \\
    %             &\underset{\text{(f)}}{=} 
    %             \frac{(\alpha_k - 1)\mu(L_k\alpha_k - \mu)}{2(L_k - \mu)}\Vert \bar x - x_{k - 1}\Vert^2
    %             + 
    %             \left(
    %                 \frac{(L_k\alpha_k - \mu)^2}{2(L_k - \mu)}
    %                 - \frac{\alpha_{k - 1}^2L_k \rho_{k - 1}(1 - \alpha_k)}{2}
    %             \right)\Vert \bar x - v_{k - 1}\Vert^2 \\ &\quad 
    %                 + \frac{\alpha_{k - 1}^2L_k \rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
    %                 + \frac{(L_k\alpha_k - \mu)\mu(1 - \alpha_k)}{L_k - \mu}\langle \bar x - x_{k - 1}, \bar x - v_{k - 1}\rangle
    %             \\
    %             &\underset{\text{(g)}}{=}
    %             \frac{(\alpha_k - 1)\mu(L_k\alpha_k - \mu)}{2(L_k - \mu)}\Vert \bar x - x_{k - 1}\Vert^2
    %             + 
    %             \frac{\mu(L_k\alpha_k - \mu)(\alpha_k - 1)}{2(L_k - \mu)}\Vert \bar x - v_{k - 1}\Vert^2
    %             \\ &\quad 
    %                 + \frac{\alpha_{k - 1}^2L_k \rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
    %                 + \frac{(L_k\alpha_k - \mu)\mu(1 - \alpha_k)}{L_k - \mu}\langle \bar x - x_{k - 1}, \bar x - v_{k - 1}\rangle
    %             \\
    %             &= \frac{\alpha_{k - 1}^2L_k \rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2 \\ & \quad
    %                 \frac{(\alpha_k - 1)\mu(L_k\alpha_k - \mu)}{2(L_k - \mu)}\left(
    %                     \Vert \bar x - x_{k - 1}\Vert^2 + \Vert \bar x - v_{k - 1}\Vert^2 - 2\langle\bar x - x_{k - 1},\bar x - v_{k - 1} \rangle
    %                 \right)
    %             \\
    %             &= \frac{\alpha_{k - 1}^2L_k \rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
    %             + \frac{(\alpha_k - 1)\mu(L_k\alpha_k - \mu)}{2(L_k - \mu)}\Vert x_{k - 1} - v_{k - 1}\Vert^2. 
    %         \end{align*}
    %         }
    %         The inequality from previously simplifies, and it has: 
    %         {\allowdisplaybreaks\small
    %         \begin{align*}
    %             0 &\le 
    %             \alpha_k F(\bar x) + (1 - \alpha_k)F(x_{k - 1}) - F(x_k)
    %             + \frac{\alpha_{k - 1}^2L_k \rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
    %             - \frac{L_k}{2}\Vert z_k - x_k\Vert^2 \\ &\quad 
    %                 + \frac{(\alpha_k - 1)\mu(L_k\alpha_k - \mu)}{2(L_k - \mu)}\Vert x_{k - 1} - v_{k - 1}\Vert^2
    %             \\
    %             &\underset{\text{(h)}}{\le}
    %             \alpha_k F(\bar x) + (1 - \alpha_k)F(x_{k - 1}) - F(x_k)
    %                 \\ &\quad
    %                 + \frac{\alpha_{k - 1}^2L_k \rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
    %                 - \frac{L_k}{2}\Vert z_k - x_k\Vert^2 
    %             \\
    %             &= (1 - \alpha_k)(F(x_{k - 1}) - F(\bar x)) + F(\bar x) - F(x_k) \\&\quad
    %                 + \frac{\alpha_{k - 1}^2L_k \rho_{k - 1}(1 - \alpha_k)}{2}\Vert \bar x - v_{k - 1}\Vert^2
    %                 - \frac{L_k}{2}\Vert z_k - x_k\Vert^2 
    %             \\
    %             &\underset{\text{(e)}}{=} 
    %             (1 - \alpha_k)\left(
    %                 F(x_{k - 1}) - F(\bar x) 
    %                 + \frac{L_k\rho_{k - 1}}{L_{k - 1}}\frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2
    %             \right) \\ &\quad
    %                 + F(\bar x) - F(x_k)-  \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
    %             \\
    %             &\le 
    %             (1 - \alpha_k)\left(
    %                 F(x_{k - 1}) - F(\bar x) 
    %                 + \max\left(1, \frac{L_k\rho_{k - 1}}{L_{k - 1}}\right)
    %                 \frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2
    %             \right) \\&\quad
    %                 + F(\bar x) - F(x_k)-  \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
    %             \\
    %             &\le (1 - \alpha_k)\left(
    %                 \max\left(1, \frac{L_k\rho_{k - 1}}{L_{k - 1}}\right)(F(x_{k - 1}) - F(\bar x))
    %                 + \max\left(1, \frac{L_k\rho_{k - 1}}{L_{k - 1}}\right)
    %                 \frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2
    %             \right) \\&\quad 
    %                 + F(\bar x) - F(x_k)-  \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2 
    %             \\
    %             &= 
    %             \max\left(1, \frac{L_k\rho_{k - 1}}{L_{k - 1}}\right)(1 - \alpha_k)\left(
    %                 F(x_{k - 1}) - F(\bar x) 
    %                 + \frac{\alpha_{k - 1}^2L_{k - 1}}{2}\Vert \bar x - v_{k - 1}\Vert^2
    %             \right) \\&\quad
    %                 + F(\bar x) - F(x_k)-  \frac{L_k\alpha_k^2}{2}\Vert \bar x - v_k\Vert^2. 
    %         \end{align*}
    %         }
    %         Finally, for the base case, when $\alpha_0 = 1$, it has $y_0 = v_{-1} = x_{-1}$, and it makes $z_0 = \bar x$ therefore this makes the proximal gradient inequality into:
    %         \begin{align*}
    %             0 &\le F(z_0) - F(x_{0}) - \frac{L_0}{2}\Vert z_0 - x_0\Vert^2 + \frac{L_0 - \mu}{2}\Vert z_0 - y_0\Vert^2
    %             \\
    %             &= F(\bar x) - F(x_0) - \frac{L_0}{2}\Vert \bar x - x_0\Vert^2 + \frac{L_0 - \mu}{2}\Vert \bar x - v_{-1}\Vert^2. 
    %         \end{align*}

    %         \par
    %         Going back to prove the intermediate results, the following will be useful. 
    %         From Definition \ref{def:st-method} it has for all $k \ge 0$
    %         \begin{align}\label{thm:onestep-napg-cnvg-i}
    %             \tau_k = L_k(1 - \alpha_k)(L_k\alpha_k - \mu)^{-1}.    
    %         \tag{i}\end{align}
    %         Then it has: 
    %         \begin{align*}\label{thm:onestep-napg-cnvg-j}
    %             (1 + \tau_k)^{-1}
    %             &\underset{\eqref{thm:onestep-napg-cnvg-i}}{=} 
    %             \left(
    %                 1 + \frac{L_k(1 - \alpha_k)}{L_k\alpha_k - \mu}
    %             \right)^{-1} = \left(
    %                 \frac{L_k\alpha_k - \mu + L_k(1 - \alpha_k)}{L_k\alpha_k - \mu}
    %             \right)^{-1}
    %             = \frac{L_k\alpha_k - \mu}{L_k - \mu}.
    %         \tag{j}\end{align*}
    %         And also
    %         \begin{align*}\label{thm:onestep-napg-cnvg-k}
    %             \tau_k(1 + \tau_k)^{-1} 
    %             &\underset{\eqref{thm:onestep-napg-cnvg-i}, \eqref{thm:onestep-napg-cnvg-j}}= 
    %             \frac{L_k(1 - \alpha_k)}{L_k\alpha_k - \mu}
    %             \frac{L_k\alpha_k - \mu}{L_k - \mu}
    %             = \frac{L_k(1 - \alpha_k)}{L_k - \mu}. 
    %         \tag{k}\end{align*}
    %         \textbf{Proof of (d)}
    %         For all $k \ge 1$, from Definition \ref{def:st-method} it has 
    %         \begin{align*}
    %             0 &= (1 + \tau_k)^{-1} v_{k - 1} + \tau_k (1 + \tau_k)^{-1} x_{k - 1} - y_k
    %             \\
    %             &\underset{\eqref{thm:onestep-napg-cnvg-k}}{=} 
    %             (1 + \tau_k)^{-1} v_{k - 1} + \frac{L_k(1 - \alpha_k)}{L_k - \mu} x_{k - 1} - y_k
    %             \\
    %             &= (1 + \tau_k)^{-1} v_{k - 1} +(1 - \alpha_k)x_{k - 1} \\ 
    %                 &\quad 
    %                 + \left(
    %                     \frac{L_k(1 - \alpha_k)}{L_k - \mu} - (1 - \alpha_k)
    %                 \right) x_{k - 1} - y_k
    %             \\
    %             &= (1 + \tau_k)^{-1} v_{k - 1} +(1 - \alpha_k)x_{k - 1}\\
    %                 &\quad 
    %                 + (1 - \alpha_k)\left(
    %                     \frac{L_k}{L_k - \mu} - 1
    %                 \right) x_{k - 1} - y_k
    %             \\
    %             &= (1 + \tau_k)^{-1} v_{k - 1} +(1 - \alpha_k)x_{k - 1} + 
    %             \frac{\mu(1 - \alpha_k)}{L - \mu}x_{k - 1} - y_k
    %             \\
    %             \iff 
    %             (1 - \alpha_k)x_{k - 1} - y_k 
    %             &= - (1 + \tau_k)^{-1}v_{k - 1} - \frac{\mu(1 - \alpha_k)}{L_k - \mu}x_{k - 1}.
    %         \end{align*}
    %         Recall the definition for $z_k$ at the start of the proof and, use the above results it yields: 
    %         \begin{align*}
    %             z_k - y_k &= \alpha_k \bar x + (1 - \alpha_k)x_{k - 1} - y_k
    %             \\
    %             &= \alpha_k \bar x - (1 + \tau_k)^{-1}v_{k - 1} - \frac{\mu(1 - \alpha_k)}{L_k - \mu}x_{k - 1}
    %             \\
    %             &\underset{\eqref{thm:onestep-napg-cnvg-j}}{=}
    %             \alpha_k \bar x - \frac{L_k\alpha_k - \mu}{L_k - \mu}v_{k - 1} 
    %             - \frac{\mu(1 - \alpha_k)}{L_k - \mu}x_{k - 1}
    %             \\
    %             &= \frac{L_k\alpha_k - \mu}{L_k - \mu}(\bar x - v_{k - 1})
    %             + \left(
    %                 \alpha_k - \frac{L_k\alpha_k - \mu}{L_k - \mu}
    %             \right)\bar x - \frac{\mu(1 - \alpha_k)}{L_k - \mu}x_{k - 1}
    %             \\
    %             &= 
    %             \frac{L_k\alpha_k - \mu}{L_k - \mu}(\bar x - v_{k - 1})
    %             +
    %             \frac{\alpha_kL_k - \alpha_k \mu - L_k\alpha_k + \mu}{L_k - \mu}
    %             \bar x - \frac{\mu(1 - \alpha_k)}{L_k - \mu}x_{k - 1}
    %             \\
    %             &= \frac{L_k\alpha_k - \mu}{L_k - \mu}(\bar x - v_{k - 1})
    %             +
    %             \frac{\mu(1 - \alpha_k)}{L_k - \mu}(\bar x - x_{k - 1}). 
    %         \end{align*}
    %         \textbf{Proof of (e)}. 
    %         The proof is direct using the equality with $x_k$ in Definition \ref{def:st-method}. 
    %         \begin{align*}
    %             z_k - x_k &= \alpha_k \bar x + (1 - \alpha_k)x_{k - 1} - x_k
    %             \\
    %             &= \alpha_k \bar x + x_{k  1} - x_k - \alpha_k x_{k - 1}
    %             \\
    %             &= \alpha_k(\bar x - \alpha_k^{-1}(x_k - x_{k - 1}) - x_{k - 1})
    %             \\
    %             &= \alpha_k (\bar x - v_k).
    %         \end{align*}
    %         \textbf{Proof of (f)}. 
    %         The proof is direct and it has: 
    %         \begin{align*}
    %             \frac{\mu^2(1 - \alpha_k)^2}{2(L_k - \mu)} - \frac{\mu\alpha_k(1 - \alpha_k)}{2}
    %             &= 
    %             \frac{1}{2(L_k - \mu)}\left(
    %                 \mu^2(1 - \alpha_k)^2 - (L_k - \mu)\mu \alpha_k(1 - \alpha_k)
    %             \right)
    %             \\
    %             &= \frac{1 - \alpha_k}{2(L_k - \mu)}\left(
    %                 \mu^2 - \mu^2\alpha_k - (L_k \mu \alpha_k - \mu^2 \alpha_k)
    %             \right)
    %             \\
    %             &= 
    %             \frac{1 - \alpha_k}{2(L_k - \mu)}\left(
    %                 \mu^2 - L_k\mu\alpha_k
    %             \right)
    %             \\
    %             &= \frac{(1 - \alpha_k)\mu(\mu - L_k\alpha_k)}{2(L_k - \mu)} 
    %             \\
    %             &= \frac{(\alpha_k - 1)\mu(L_k\alpha_k - \mu)}{2(L_k - \mu)}. 
    %         \end{align*}
    %         \textbf{Proof of (g)}
    %         The proof is direct: 
    %         \begin{align*}
    %             \frac{(L_k\alpha_k - \mu)^2}{2(L_k - \mu)} - \frac{\alpha_{k - 1}^2 L_k \rho_{k - 1}(1 - \alpha_k)}{2}
    %             &\underset{\text{(c)}}{=} \frac{(L\alpha_k - \mu)^2}{2(L_k - \mu)} - \frac{L_k\alpha_k(\alpha_k - \mu/L_k)}{2}
    %             \\
    %             &= \frac{1}{2(L_k - \mu)}\left(
    %                 (L_k\alpha_k - \mu)^2 - (L_k - \mu)L_k\alpha_k(\alpha_k - \mu/L_k)
    %             \right)
    %             \\
    %             &= 
    %             \frac{1}{2(L_k - \mu)}\left(
    %                 (L_k\alpha_k - \mu)^2 - (L_k - \mu)\alpha_k(L_k\alpha_k - \mu)
    %             \right)
    %             \\

>>>>

        \begin{definition}[similar triangle representation of NAPG]\;\label{def:st-method}\\
            Let $(\alpha_k)_{k \ge 0}$ be an R-WAPG sequence. 
            Suppose that the base case $v_{-1}, x_{k - 1}\in \RR^n$ is given to initialize the algorithm. 
            Then the algorithm produces the sequence of iterates $(y_k, x_k, v_k)_{k \ge 0}$ and auxiliary parameter sequence $L_k, \tau_k$ satisfying these inequalities: 
            \begin{align*}
                & \tau_k = L_k(1 - \alpha_k)(L_k\alpha_k - \mu)^{-1}, 
                \\
                & y_k = (1 + \tau_k)^{-1} v_{k - 1} + \tau_k (1 + \tau_k)^{-1} x_{k - 1},
                \\
                & D_f(x_k, y_k) \le L_k/2\Vert x_k - y_k\Vert^2, 
                \\
                & x_k = T_{L_k}(y_k),
                \\
                & v_k = x_{k - 1} + \alpha_k^{-1}(x_k - x_{k - 1}). 
            \end{align*} 
        \end{definition}
        The following theorems are critical in analyzing the behavior of algorithm in Definition \ref{def:st-method}. 
        \begin{theorem}[proximal gradient inequality]\label{thm:pg-ineq}
            Let function $F$ satisfies Assumption \ref{ass:smooth-plus-nonsmooth}, so it's $\mu \ge 0$ strongly convex. 
            For all $x\in \RR^n$, define $x^+ = T_L(x)$, then there exists a $B \ge 0$ such that $D_f(x^+, x) \le B/2 \Vert x^+ - x\Vert^2$. 
            Then, for all $z \in \RR^n$ it satisfies proximal gradient inequality at point $x$:  
            \begin{align*}
                0&\le F(z) - F(x^+) - \frac{B}{2}\Vert z - x^+\Vert^2  + \frac{B - \mu}{2}\Vert z - x\Vert^2
                \\
                &=  F(z) - F(x^+) - \langle B(x - x^+), z - x\rangle
                - \frac{\mu}{2}\Vert z - x\Vert^2
                - \frac{B}{2}\Vert x - x^+\Vert^2. 
            \end{align*}
            Since $f$ is assumed to be $L$ Lipschitz smooth, the above condition is true for all $x, y \in \RR^n$ for all $B \ge L$. 
        \end{theorem}
        \begin{remark}
            The theorem is the same as in Nesterov's book \cite[Theorem 2.2.13]{nesterov_lectures_2018}, but with the use of proximal gradient mapping and proximal gradient instead of project gradient hence making it equivalent to the theorem in Beck's book \cite[Theorem 10.16]{beck_first-order_2017}. 
            The only generalization here is parameter $B$ which made to accommodate algorithm that implements Definition \ref{def:st-method} with some line search routine. 
            Each of the reference books gives a proof of the theorem. 
            But for the best consistency in notations, see Theorem 2.3 in Li and Wang \cite{li_relaxed_2025}. 
        \end{remark}
        \begin{theorem}[Jensen's inequality]\label{thm:jesen}
            Let $F: \RR^n \rightarrow \overline \RR$ be a $\mu \ge 0$ strongly convex function. 
            Then, it is equivalent to the following condition. 
            For all $x, y \in \RR^n$, $\lambda \in (0, 1)$ it satisfies the inequality 
            \begin{align*}
                (\forall \lambda \in [0, 1])\; 
                F(\lambda x + (1 - \lambda)y) \le \lambda F(x) + (1 - \lambda)F(y) -\frac{\mu\lambda(1 - \lambda)}{2} \Vert y - x\Vert^2. 
            \end{align*}
        \end{theorem}
        \begin{remark}
            If $x, y$ is out of $\dom F$, the inequality still work by convexity. 
        \end{remark}

    \subsection{Stochastic accelerated proximal gradient}
        The following assumption about the objective function is fundamental in incremental gradient method for Machine Learning, data science other similar tasks. 
        \begin{assumption}[sum of many]\label{ass:sum-of-many}
            Define $F := (1/n)\sum_{i = 1}^{n} F_i$ where $F_i = f_i + g_i$.
            Assume that for all $i = 1, \ldots, n$, each $f_i:\RR^n \rightarrow \RR$ are $K^{(i)}$ smooth and $\mu^{(i)} \ge 0$ strongly convex function such that $K^{(i)} > \mu^{(i)}$ and, $g:\RR^n \rightarrow \overline \RR$ is a closed convex proper function. 
            Consequently, the function $f$ can be written as $F = g + f$ with $f = (1/n)\sum_{i = 1}^{n} f_i, g = (1/n)\sum_{i = 1}^{n}f_i + g_i$ there, it also satisfies Assumption \ref{ass:smooth-plus-nonsmooth} with $L = (1/2)\sum_{i = 1}^n K^{(i)}$ and $\mu = (1/n)\sum_{i = 1}^{n}\mu^{(i)}$. 
        \end{assumption}
        This assumption is stronger than Assumption \ref{ass:smooth-plus-nonsmooth}. 
        It still appears everywhere in practice, for example if $F_i$ are all indicator function of convex set, then it solves feasibility problem $\bigcap_{i = 1}^n C_i$ and, in this case, the proximal gradient operator becomes a projection onto the convex set $C_i$. 
        In practice, each of the strong convexity constant $\mu^{(i)}$ may not be easily accessible. 
        And we further note that if $\mu > 0$ strongly convex, then there exists at least one $\mu^{(i)} \ge 0$. 
        The interpolation hypothesis from Machine Learning stated that the model has the capacity to perfect fit all the observed data. 
        \begin{assumption}[interpolation hypothesis]\label{ass:interp-hypothesis}
            Suppose that $F := (1/n)\sum_{i = 1}^{n} F_i$ satisfying Assumption \ref{ass:sum-of-many}. 
            In addition, assuming that it has $0 = \inf_{x}F(x)$ and, there exists some $\bar x \in \RR^n$ such that for all $i = 1, \ldots, n$ it satisfies $0 = f_i(\bar x)$. 
            Obviously, all such $\bar x$ forms the set of minimizers of $F$. 
        \end{assumption}
        \begin{definition}[SNAPG-V2]\label{def:snapg-v2}
            Let $F$ satisfies Assumption \ref{ass:sum-of-many}. 
            Let $(I_k)_{k \ge 0}$ be a list of i.i.d random variables uniformly sampled from set $\{0, 1, 2, \cdots, n\}$. 
            Initialize $v_{-1} = x_{-1}, \alpha_0 = 1$. 
            The SNAPG generates the sequence $(y_k, x_k, v_k)_{k \ge 0}$ such that for all $k \ge 0$ they satisfy: 
                & (L_{k - 1}/L_k)(1 - \alpha_{k})\alpha_{k - 1}^2 = \alpha_{k}\left(\alpha_{k} - \mu/L_k\right), \\
                & \tau_k = L_k(1 - \alpha_k)\left(L_k \alpha_k - \mu^{(I_k)}\right)^{-1}, \\
                & y_k = (1 + \tau_k)^{-1}v_{k - 1} + \tau_k(1 + \tau_k)^{-1}x_{k - 1}, \\
                & x_k =  T_{L_k}(y_k | F_{I_k}) \text{ s.t: } D_f(x_k, y_k) \le L_k/2\Vert y_k - x_k\Vert^2, \\
                & v_k = x_{k - 1} + \alpha_k^{-1}(x_k - x_{k - 1}). 
        \end{definition}
        \begin{lemma}[range of the momentum sequence in SNAPG-V2]\;\label{lemma:snapg-v2-seq-range}\\
            Suppose that $(L_k)_{k \ge 0}$ is a sequence such that $L_k > 0$ for all $k \ge 0$. 
            Let $(\alpha_k)_{k \ge 0}$ be a sequence such that $\alpha_0 \in (0, 1]$ and, for all $k \ge 1$, it's recursively satisfies equality: 
                (L_{k - 1}/L_k)(1 - \alpha_{k})\alpha_{k - 1}^2 = \alpha_{k}\left(\alpha_{k} - \mu/L_k\right). 
            And, the following items are true: 
            \begin{enumerate}
                \item Solution to the equation with $\alpha_k > 0$ is given by: 
                    \alpha_k = \frac{L_{k - 1}}{2L_k} \left(
                        - \alpha_{k - 1}^2 + \frac{\mu}{L_{k - 1}}
                        + \sqrt{
                                \alpha_{k - 1} - \frac{\mu}{L_{k - 1}}
                            \right)^2
                            + \frac{4\alpha_{k - 1}^2L_k}{L_{k - 1}}
                    \right). 
                \item ... \todoinline{This part is not finished yet. }
            \end{enumerate}
        \end{lemma}
        \newpage
